Code Club Project: Assessing whether intra and inter-genomic variation hinder utility of ESVs and ASVs

### 2021-02-19 submission/manuscript.tex
First round of revisions

\hypertarget{amplicon-sequence-variants-artificially-split-bacterial-genomes-into-separate-units-of-inference}{%
\section{Amplicon sequence variants artificially split bacterial genomes
into separate units of
inference}\label{amplicon-sequence-variants-artificially-split-bacterial-genomes-into-separate-units-of-inference}}

@@

Amplicon sequencing variants (ASVs) have been proposed as an alternative
to operational taxonomic units (OTUs) for analyzing microbiomes. ASVs
have grown in popularity, in part, because of a desire to reflect a more
refined level of taxonomy because they do not cluster sequences based on
a distance-based threshold. However, ASVs and the use of overly narrow
thresholds to identify OTUs increases the risk of splitting a single
genome into separate clusters. I addressed this problem by analyzing the
intragenomic variation of 16S rRNA genes from the bacterial genomes
represented in the rrn copy number database, which contained
\textbf{15,614} genomes from \textbf{4,774} species. The analysis
confirmed the severity of this risk. As the number of copies of the 16S
rRNA gene increased in a genome, the number of ASVs also increased. For
full length 16S rRNA genes, there was an average of \textbf{0.60} ASVs
per copy of the 16S rRNA gene. Among genomes with 7 copies of the 16S
rRNA, such as \emph{E. coli}, it was necessary to use a distance
threshold of \textbf{5.5}\% to cluster the ASVs from the same genome
into a single OTU. This research highlights the risk of splitting a
single bacterial genome into separate clusters when ASVs are used to
analyze 16S rRNA gene sequence data. Although there is also a risk of
clustering different species into the same OTU, the effects of those
risks on biological inferences are less than those from artificially
splitting a genome into separate ASVs and OTUs.

@@

16S rRNA gene sequencing is a powerful technique for describing and
comparing microbial communities (1). Efforts to link 16S rRNA gene
sequences to taxonomic levels based on distance thresholds go back to at
least the 1990s. The distance-based thresholds that were developed and
are now widely used (3\%) were based on DNA-DNA hybridization approaches
that are not as precise as genome sequencing (2, 3). Instead, genome
sequencing technologies have suggested that the widely used 3\% distance
threshold to operationally define bacterial taxa is too coarse (4--6).
As an alternative to OTUs, amplicon sequencing variants (ASVs) have been
proposed as a way to adopt the thresholds suggested by genome sequencing
to microbial community analysis using 16S rRNA gene sequences (7--10).
ASVs are a unit of microbial community inference that do not cluster
sequences based on a distance-based threshold (11). However, most
bacterial genomes have more than 1 copy of the rrn operon and those
copies are not identical (12, 13). Therefore, using too fine a threshold
to identify OTUs creates the risk of splitting a single genome into
multiple bins and using too broad of a threshold to define OTUs creates
the risk of lumping together bacterial species into the same OTU. An
example of both is seen in the comparison of \emph{Staphylococcus
aureus} (NCTC 8325) and \emph{S. epidermidis} (ATCC 12228) where each
genome has 5 copies of the 16S rRNA gene. The 10 copies of the 16S rRNA
gene each have a different sequence and so if OTUs are defined based on
ASVs, each genome would be split into 5 OTUs. Conversely, if the copies
were clustered using a 3\% distance threshold all 10 copies would
cluster into the same OTU. The goal of this study was to quantify the
risk of splitting a single genome into multiple bins and the risk of
lumping together different bacterial species into the same bin.

To investigate the variation in the number of copies of the 16S rRNA
gene per genome as well as the intragenomic variation among copies of
the 16S rRNA gene, I obtained reference 16S rRNA sequences from the rrn
copy number database (rrnDB)(14). Among the \textbf{4,774} species
represented in the rrnDB there were \textbf{15,614} genomes. The median
number of rrn operson per species ranged between \textbf{1} (e.g.,
\textbf{\emph{Mycobacterium tuberculosis}}) and \textbf{19}
(\textbf{\emph{Metabacillus litoralis}}) copies of the rrn operon. As
the number of copies of the operon in a genome increased, the number of
variants of the 16S rRNA gene in each genome also increased. On average,
there were \textbf{0.60} variants per copy of the full length 16S rRNA
gene and an average of \textbf{0.26}, \textbf{0.33}, and \textbf{0.27}
variants when considering the V4, V3-V4, and V4-V5 regions of the gene,
respectively. Although a species tended to have a consistent number of
16S rRNA gene copies per genome, the number of total variants increased
with the number of genomes that were sampled (\textbf{Figure 1}). For
example, \textbf{\emph{Mycobacterium tuberculosis}} generally only had
\textbf{1} copy of the gene per genome, but across the \textbf{180}
genomes that have been sequenced there were \textbf{11} versions of the
gene. Similarly, a \emph{E. coli} genome typically had \textbf{7} copies
of the 16S rRNA gene with between \textbf{6} and \textbf{10} distinct
full length sequences per genome. Across the \textbf{958} \emph{E. coli}
genomes that have been sequenced, there were \textbf{1,013} different
variants of the gene. These observations highlight the risk of selecting
a threshold for defining units of inference that is too narrow because
it is possible to split a single genome into multiple units.

A method to avoid splitting a single genome into multiple units of
inference is to cluster together similar 16S rRNA gene sequences.
Therefore, I assessed the impact of the distance threshold used to
define clusters of 16S rRNA genes on the propensity to split a genome
into separate clusters. I observed that as the number of copies of the
\emph{rrn} operon increased, the distance threshold required to reduce
the ASVs in each genome to a single OTU increased (Figure 1). Among
species with 7 copies of the \emph{rrn} operon (e.g., \emph{E. coli}), I
found that a threshold of \textbf{5.5}\% was required to reduce full
length ASVs to a single OTU in 95\% of the species. Similarly,
thresholds of \textbf{2.5}, \textbf{4.0}, and \textbf{3.5}\% were
required for the V4, V3-V4, and V4-V5 regions, respectively. But, if a
3\% distance threshold was used, then ASVs from genomes containing fewer
than \textbf{5}, \textbf{8}, \textbf{6}, and \textbf{6} copies of the
\emph{rrn} operon would reliably be clustered into a single OTU for ASVs
from the V1-V9, V4, V3-V4, and V4-V5 regions, respectively.
Consequently, these results demonstrate that broad thresholds must be
used to avoid splitting different operons from the same genome into
separate clusters.

At broad thresholds multiple species could be represented by the same
OTU (\textbf{Figure 2}). Using ASVs, \textbf{3.6}\% of the species
shared a 16S rRNA gene sequence variant with another species when
considering full length sequences and \textbf{14.9}, \textbf{10.2}, and
\textbf{12.0}\% when considering the V4, V3-V4, and V4-V5 regions,
respectively. At the commonly used 3\% threshold, \textbf{25.2}\% of the
species shared an OTU when considering full length sequences and
\textbf{33.0}, \textbf{29.4}, and \textbf{32.2}\% when considering the
V4, V3-V4, and V4-V5 regions, respectively. Considering that species
designations are unevenly applied and reflect multiple biases, the risk
of splitting a genome into multiple OTUs more problematic than
clustering species together. Therefore, larger thresholds are advisable.

The results of this analysis demonstrate that there is a significant
risk of splitting single genomes into multiple bins if too fine of a
threshold is applied to defining an OTU. An ongoing problem for
amplicon-based studies is defining a meaningful taxonomic unit of
inference (11, 15, 16). Since there is no consensus definition for a
biological species concept (17, 18), microbiologists must accept that
how we have named bacterial species is biased and that taxonomic rules
are not applied in a consistent manner (e.g., (19)). This makes it more
challenging to attempt to fit a distance threshold to define an OTU
definition that matches a set of species names (20). Furthermore, the
16S rRNA gene does not evolve at the same rate across all bacterial
lineages (15), which limits the biological interpretation of a common
OTU definition. A distance-based definition of a taxonomic unit based on
16S rRNA gene or full genome sequences is, at best, operational and not
grounded in biological theory (15, 21--23). There is general agreement
in bacterial systematics that to classify something to a bacterial
species, you need phenotypic and genome sequence data (17--19). We are
asking too much of a short section of a bacterial genome to be able to
differentiate between species. It is difficult to defend a unit of
inference that would split a single genome into multiple taxonomic
units. It is not biologically plausible to entertain the possibility
that parts of a genome would have different ecologies. Although there
are multiple reasons that proponents of ASVs encourage their use, the
significant risk of splitting genomes is too high to warrant their use.

\textbf{Materials and Methods. (i) Data availability.} The 16S rRNA gene
sequences used in this study were obtained from the \emph{rrn}DB
(\url{https://rrndb.umms.med.umich.edu}; version 5.6, released November
8, 2019) (14). At the time of submission, this is the most current
version of the database. The \emph{rrn}DB obtained the curated 16S rRNA
gene sequences from the KEGG database, which ultimately obtained them
from NCBI's non-redundant RefSeq database. The \emph{rrn}DB provides
downloadable versions of the sequences with their taxonomy as determined
using the naive Bayesian classifier trained on the RDP reference
taxonomy. For some genomes this resulted in multiple classifications
since a genome's 16S rRNA gene sequences were not identical. Instead, I
mapped the RefSeq accession number for each genome in the database to
obtain a single taxonomy for each genome. Because strain names were not
consistently given to genomes across bacterial species, the strain level
designations were ignored.

\textbf{(ii) Definition of regions within 16S rRNA gene.} The full
length 16S rRNA gene sequences were aligned to a SILVA reference
alignment of the 16S rRNA gene (v138) using the mothur software package
(v. 1.XX) (24, 25). Regions of the 16S rRNA gene were selected because
of their use in the microbial ecology literature. Full length sequences
corresponded to \emph{E. coli} positions XX through XXXX, V4 to
positions XXX through XXX, V3-V4 to positions XXX through XXX, and V4-V5
to positions XXX through XXX.

\textbf{(iii) Controlling for uneven sampling of genomes by species.}
Because of the uneven distribution of genome sequences across species,
for the analysis of splitting genomes and lumping species I randomly
selected one genome for each species. The random selection was repeated
100 times. Analyses based on this randomization report the median of the
100 randomizations. The intraquartile range between randomizations was
typically less than XXXX. Because it was so small, confidence intervals
are not included in Figure 2.

\textbf{(iv) Reproducible data analysis.} The code to perform the
analysis in this manuscript and its hisotry are available as a git-based
version control repository on GitHub
(\url{https://github.com/pschloss/Schloss_rrnAnalysis_XXXX_2020}). The
analysis can be regenerated using a GNU Make-based workflow that made
use of built-in bash tools (v. 3.2.57), mothur (v. 1.XX), and R (v.
4.X.X). Within R, I used the tidyverse (v. 4.X.X), data.table (v.
4.X.X), Rcpp (v. 4.X.X), furrr (v. 4.X.X), and rmarkdown (v. 4.X.X)
packages. The conception and development of this analysis is available
as a playlist on the Riffomonas YouTube channel
(\url{https://www.youtube.com/playlist?list=PLmNrK_nkqBpKY3SZiivlIGvcLX-KHmfR8}).

\textbf{Acknowledgements.} I am grateful to Robert Hein and Thomas
Schmidt who maintain the rrnDB for their help in understanding the
curation of the database and for making the 16S rRNA gene sequences and
related metadata publicly available. I am also grateful to community
members who watched the serialized version of this analysis on YouTube
and provided their suggestions and questions.

@@

\textbf{Figure 1. The distance threshold required to prevent the
splitting of genomes into multiple OTUs increases as the number of
\emph{rrn} operons in the genome increases.} Each line represents the
median distance threshold for each region of the 16S rRNA gene that is
required for 95\% of the species with the indicated numbrer of
\emph{rrn} operons to cluster their ASVs to a single OTU. The median
distance threshold was calculated across 100 randomizations in which one
genome was sampled from each species. Only those number of \emph{rrn}
operons that were found in more than 100 species are included.

@@

\textbf{Figure 2. As the distance threshold used to define an OTU
increases, the fraction of genomes split into separate OTUs decreases
while the fraction of species that are merged into the same OTU
increases.} These data represent the median fractions for both
measurements across 100 randomizations. In each randomization, one
genome was sampled from each species.

@@

\textbf{Figure S1. The ratio of number of distinct ASVs per copy of the
\emph{rrn} operon increases for a species as the number of genomes
sampled increases.} Each point represents a different species and is
shaded to be 80\% transparent so that when points overlap they become
darker. The blue line represents a smoothed fit through the data.

>>>>

\hypertarget{amplicon-sequence-variants-artificially-split-bacterial-genomes-into-separate-clusters}{%
\section{Amplicon sequence variants artificially split bacterial genomes
into separate
clusters}\label{amplicon-sequence-variants-artificially-split-bacterial-genomes-into-separate-clusters}}

@@

Amplicon sequencing variants (ASVs) have been proposed as an alternative
to operational taxonomic units (OTUs) for analyzing microbiomes. ASVs
have grown in popularity, in part, because of a desire to reflect a more
refined level of taxonomy because they do not cluster sequences based on
a distance-based threshold. However, ASVs and the use of overly narrow
thresholds to identify OTUs increases the risk of splitting a single
genome into separate clusters. I assessed this problem by analyzing the
intragenomic variation of 16S rRNA genes from the bacterial genomes
represented in a \emph{rrn} copy number database, which contained
\textbf{15,614} genomes from \textbf{4,774} species. As the number of
copies of the 16S rRNA gene increased in a genome, the number of ASVs
also increased. There was an average of \textbf{0.60} ASVs per copy of
the 16S rRNA gene, for full length 16S rRNA genes. It was necessary to
use a distance threshold of \textbf{5.5}\% to cluster the ASVs from the
same genome into a single OTU, for genomes with 7 copies of the 16S
rRNA, such as \emph{E. coli}. This research highlights the risk of
splitting a single bacterial genome into separate clusters when ASVs are
used to analyze 16S rRNA gene sequence data. Although there is also a
risk of clustering different species into the same OTU, the effects of
those risks on biological inferences are less than those from
artificially splitting a genome into separate ASVs and OTUs.

@@

16S rRNA gene sequencing is a powerful technique for describing and
comparing microbial communities (1). Efforts to link 16S rRNA gene
sequences to taxonomic levels based on distance thresholds go back to at
least the 1990s. The distance-based thresholds that were developed and
are now widely used (i.e., 3\%) were based on DNA-DNA hybridization
approaches that are not as precise as genome sequencing (2, 3). Instead,
genome sequencing technologies have suggested that the widely used 3\%
distance threshold to operationally define bacterial taxa is too coarse
(4--6). As an alternative to OTUs, amplicon sequencing variants (ASVs)
have been proposed as a way to adopt the thresholds suggested by genome
sequencing to microbial community analysis using 16S rRNA gene sequences
(7--10). ASVs are a unit of microbial community inference that do not
cluster sequences based on a distance-based threshold (11). However,
most bacterial genomes have more than 1 copy of the \emph{rrn} operon
and those copies are not identical (12, 13). Therefore, using too fine a
threshold to identify OTUs creates the risk of splitting a single genome
into multiple bins and using too broad of a threshold to define OTUs
creates the risk of lumping together bacterial species into the same
OTU. An example of both is seen in the comparison of
\emph{Staphylococcus aureus} (NCTC 8325) and \emph{S. epidermidis} (ATCC
12228) where each genome has 5 copies of the 16S rRNA gene. Each of the
10 copies of the 16S rRNA gene in these two genomes were distinct and
would yield 10 ASVs. Conversely, if the copies were clustered using a
3\% distance threshold, then all 10 ASVs would cluster into the same
OTU. The goal of this study was to quantify the risk of splitting a
single genome into multiple clusters and the risk of lumping together
different bacterial species into the same cluster.

To investigate the variation in the number of copies of the 16S rRNA
gene per genome as well as the intragenomic variation among copies of
the 16S rRNA gene, I obtained reference 16S rRNA sequences from the
\emph{rrn} copy number database (\emph{rrn}DB)(14). Among the
\textbf{4,774} species represented in the \emph{rrn}DB there were
\textbf{15,614} genomes. The median number of \emph{rrn} operons per
species ranged between \textbf{1} (e.g., \textbf{\emph{Mycobacterium
tuberculosis}}) and \textbf{19} (\textbf{\emph{Metabacillus litoralis}})
copies of the \emph{rrn} operon. As the number of copies of the operon
in a genome increased, the number of variants of the 16S rRNA gene in
each genome also increased. On average, there were \textbf{0.60}
variants per copy of the full length 16S rRNA gene and an average of
\textbf{0.26}, \textbf{0.33}, and \textbf{0.27} variants when
considering the V4, V3-V4, and V4-V5 regions of the gene, respectively.
Although a species tended to have a consistent number of 16S rRNA gene
copies per genome, the number of total variants increased with the
number of genomes that were sampled (\textbf{Figure 1}). For example,
\textbf{\emph{Mycobacterium tuberculosis}} generally only had \textbf{1}
copy of the gene per genome, but across the \textbf{180} genomes in the
\emph{rrn}DB there were \textbf{11} versions of the gene. Similarly, a
\emph{E. coli} genome typically had \textbf{7} copies of the 16S rRNA
gene with between \textbf{6} and \textbf{10} distinct full length
sequences per genome. Across the \textbf{958} \emph{E. coli} genomes in
the \emph{rrn}DB, there were \textbf{1,013} different variants of the
gene. These observations highlight the risk of selecting a threshold for
defining clusters that is too narrow because it is possible to split a
single genome into multiple clusters.

A method to avoid splitting a single genome into multiple clusters is to
cluster 16S rRNA gene sequences together based on their similarity to
each other. Therefore, I assessed the impact of the distance threshold
used to define clusters of 16S rRNA genes on the propensity to split a
genome into separate clusters. I observed that as the number of copies
of the \emph{rrn} operon increased, the distance threshold required to
reduce the ASVs in each genome to a single OTU increased (Figure 1).
Among species with 7 copies of the \emph{rrn} operon (e.g., \emph{E.
coli}), I found that a threshold of \textbf{5.5}\% was required to
reduce full length ASVs to a single OTU in 95\% of the species.
Similarly, thresholds of \textbf{2.5}, \textbf{4.0}, and \textbf{3.5}\%
were required for the V4, V3-V4, and V4-V5 regions, respectively. But,
if a 3\% distance threshold was used, then ASVs from genomes containing
fewer than \textbf{5}, \textbf{8}, \textbf{6}, and \textbf{6} copies of
the \emph{rrn} operon would reliably be clustered into a single OTU for
ASVs from the V1-V9, V4, V3-V4, and V4-V5 regions, respectively.
Consequently, these results demonstrate that broad thresholds must be
used to avoid splitting different operons from the same genome into
separate clusters. At broad thresholds multiple species could be
represented by the same OTU (\textbf{Figure 2}). Using ASVs,
\textbf{3.6}\% of the species shared a 16S rRNA gene sequence variant
with another species when considering full length sequences and
\textbf{14.9}, \textbf{10.2}, and \textbf{12.0}\% when considering the
V4, V3-V4, and V4-V5 regions, respectively. At the commonly used 3\%
threshold, \textbf{25.2}\% of the species shared an OTU with another
speecies when considering full length sequences and \textbf{33.0},
\textbf{29.4}, and \textbf{32.2}\% when considering the V4, V3-V4, and
V4-V5 regions, respectively. Considering that species designations are
unevenly applied and reflect multiple human-imposed biases, the risk of
splitting a genome into multiple OTUs more problematic than clustering
species together. Therefore, larger thresholds are advisable.

The results of this analysis demonstrate that there is a significant
risk of splitting a single genome into multiple clusters if too fine of
a threshold is applied to defining an OTU. An ongoing problem for
amplicon-based studies is defining a meaningful taxonomic unit (11, 15,
16). Since there is no consensus definition for a biological species
concept (17, 18), microbiologists must accept that how we have named
bacterial species is biased and that taxonomic rules are not applied in
a consistent manner (e.g., (19)). This makes it impossible to fit a
distance threshold to define an OTU definition that matches a set of
species names (20). Furthermore, the 16S rRNA gene does not evolve at
the same rate across all bacterial lineages (15), which limits the
biological interpretation of a common OTU definition. A distance-based
definition of a taxonomic unit based on 16S rRNA gene or full genome
sequences is, at best, operational and not grounded in biological theory
(15, 21--23). There is general agreement in bacterial systematics that
to classify something to a bacterial species, phenotypic and genome
sequence data are needed (17--19). A short section of a bacterial genome
simply cannot differentiate between species. Moreover, it is difficult
to defend a clustering approach that would split a single genome into
multiple taxonomic units. It is not biologically plausible to entertain
the possibility that parts of a genome would have different ecologies.
Although there are multiple reasons that proponents favor ASVs, the
significant risk of artificially splitting genomes into separate
clusters is too high to warrant their use.

\textbf{Materials and Methods. (i) Data availability.} The 16S rRNA gene
sequences used in this study were obtained from the \emph{rrn}DB
(\url{https://rrndb.umms.med.umich.edu}; version 5.6, released November
8, 2019) (14). At the time of submission, this was the most current
version of the database. The \emph{rrn}DB obtained the curated 16S rRNA
gene sequences from the KEGG database, which ultimately obtained them
from NCBI's non-redundant RefSeq database. The \emph{rrn}DB provided
downloadable versions of the sequences with their taxonomy as determined
using the naive Bayesian classifier trained on the RDP reference
taxonomy. For some genomes this resulted in multiple classifications
since a genome's 16S rRNA gene sequences were not identical. Instead, I
mapped the RefSeq accession number for each genome in the database to
obtain a single taxonomy for each genome. Because strain names were not
consistently given to genomes across bacterial species, the strain level
designations were ignored.

\textbf{(ii) Definition of regions within 16S rRNA gene.} The full
length 16S rRNA gene sequences were aligned to a SILVA reference
alignment of the 16S rRNA gene (v. 138) using the mothur software
package (v. 1.44.2) (24, 25). Regions of the 16S rRNA gene were selected
because of their use in the microbial ecology literature. Full length
sequences corresponded to \emph{E. coli} str. K-12 substr. MG1655
(NC\_000913) positions 28 through 1491, V4 to positions 534 through 786,
V3-V4 to positions 358 through 786, and V4-V5 to positions 534 through
908.

\textbf{(iii) Controlling for uneven sampling of genomes by species.}
Because of the uneven distribution of genome sequences across species,
for the analysis of splitting genomes and lumping species I randomly
selected one genome for each species. The random selection was repeated
100 times. Analyses based on this randomization reported the median of
the 100 randomizations. The intraquartile range between randomizations
was less than XXXX. Because the range was so small, the confidence
intervals were smaller than the thickness of the lines in Figures 1 and
2 and were not included.

\textbf{(iv) Reproducible data analysis.} The code to perform the
analysis in this manuscript and its history are available as a git-based
version control repository on GitHub
(\url{https://github.com/SchlossLab/Schloss_rrnAnalysis_mSphere_2021}).
The analysis can be regenerated using a GNU Make-based workflow that
made use of built-in bash tools (v. 3.2.57), mothur (v. 1.44.2), and R
(v. \textbf{4.0.3}). Within R, I used the tidyverse (v. \textbf{1.3.0}),
data.table (v. \textbf{1.13.2}), Rcpp (v. packageVersion(``Rcpp'')),
furrr (v. packageVersion(``furrr'')), and rmarkdown (v.
packageVersion(``rmarkdown'')) packages. The conception and development
of this analysis is available as a playlist on the Riffomonas YouTube
channel
(\url{https://youtube.com/playlist?list=PLmNrK_nkqBpL7m_tyWdQgdyurerttCsPY}).

\textbf{Acknowledgements.} I am grateful to Robert Hein and Thomas
Schmidt, who maintain the \emph{rrn}DB, for their help in understanding
the curation of the database and for making the 16S rRNA gene sequences
and related metadata publicly available. I am also grateful to community
members who watched the serialized version of this analysis on YouTube
and provided suggestions and questions over the course of the
development of this project.

@@

\textbf{Figure 1. The distance threshold required to prevent the
splitting of genomes into multiple OTUs increased as the number of
\emph{rrn} operons in the genome increased.} Each line represents the
median distance threshold for each region of the 16S rRNA gene that is
required for 95\% of the species with the indicated numbrer of
\emph{rrn} operons to cluster their ASVs to a single OTU. The median
distance threshold was calculated across 100 randomizations in which one
genome was sampled from each species. Only those number of \emph{rrn}
operons that were found in more than 100 species are included.

@@

\textbf{Figure 2. As the distance threshold used to define an OTU
increased, the fraction of genomes split into separate OTUs decreased
while the fraction of species that were merged into the same OTU
increases.} These data represent the median fractions for both
measurements across 100 randomizations. In each randomization, one
genome was sampled from each species.

@@

\textbf{Figure S1. The ratio of number of distinct ASVs per copy of the
\emph{rrn} operon increased for a species as the number of genomes
sampled increased.} Each point represents a different species and was
shaded to be 80\% transparent so that when points overlap they become
darker. The blue line represents a smoothed fit through the data.
